Calculating Entropies With Nested Sampling

### 2017-01-17 paper/ms.tex
Numbers
Another number
Calculated mutual info and it is wrong. Need to figure out why

\begin{align}
H_{\x}     &= 7.345 \pm 0.027 \\  % (max depth was 30)
H_{\d}     &= 
H_{\x, \d} &=    
\end{align}

@@

>>>>

\begin{align}
H_{\x}     &= 7.345  \pm 0.027 \\  % max depth was 30
H_{\d}     &= 703.96 \pm 0.31  \\  % max depth was 1000
H_{\x, \d} &= 712.27 \pm 0.31      % max depth was 1000
\end{align}

@@

Converting these to differential entropies, we obtain
\begin{align}
H'_{\x}     &= 1.131  \pm 0.027 \\  % max depth was 30
H'_{\d}     &= 697.75 \pm 0.31  \\  % max depth was 1000
H'_{\x, \d} &= 699.84 \pm 0.31      % max depth was 1000
\end{align}
and therefore a mutual information of {\query a negative value! Oh dear!
Something is wrong.}
